\begin{English}
    \chapter*{Acknowledgments}
\end{English}

\begin{Russian}
    \chapter*{Благодарности}
\end{Russian}

%The online English version of this book is currently publicly available and open-source.
\begin{English}
    In the process of writing this book, a large number of documents and papers have been referenced. Most of the theoretical knowledge of mathematics is the result of previous research, not my original creation. A small part of the experimental design also comes from various open-source code demonstration programs, but most of them are written by myself. In addition, there are some pictures taken from published journals or conference papers, which have been cited in the text. Unexplained images are either original or fetched from the Internet. I don’t want to infringe anyone’s picture copyright. If readers find any problems, please contact me to modify it.
\end{English}

\begin{Russian}
    В процессе написания этой книги было использовано большое количество документов и статей. Большая часть теоретических знаний по математике является результатом предыдущих исследований, а не моим оригинальным творением. Небольшая часть экспериментального дизайна также взята из различных демонстрационных программ с открытым исходным кодом, но большинство из них написано мной. Кроме того, есть некоторые фотографии, взятые из опубликованных журналов или материалов конференций, которые цитируются в тексте. Изображения без указания источника являются либо оригинальными, либо взятыми из Интернета. Я не хочу нарушать чьи-либо авторские права на изображения. Если читатели обнаружат какие-либо проблемы, пожалуйста, свяжитесь со мной, чтобы это исправить.
\end{Russian}

\begin{English}
    As I'm not a native English speaker, the translation work is based on Google translation and some afterward modifications. If you think the quality of translation can be improved and willing to do this, please contact me or send an issue on Github. Any help will be welcome!
\end{English}

\begin{Russian}
    Поскольку я не являюсь носителем английского языка, работа по переводу основана на переводе Google с некоторыми последующими изменениями. Если вы считаете, что качество перевода можно улучшить и хотите это сделать, свяжитесь со мной или отправьте вопрос на Github. Любая помощь будет приветствоваться!
\end{Russian}

\begin{English}
    Thanks for the following friend's help in the translation time: Nicolas Rosa, Carrie (Yan Ran), Collen Jones, Hong Ma. And also, thanks for your attention and support!

    Please contact me through GitHub or email: \href{mailto:gao.xiang.thu@gmail.com}{gao.xiang.thu@gmail.com}.
\end{English}

\begin{Russian}
    Спасибо за помощь во время перевода следующим друзьям: Nicolas Rosa, Carrie (Yan Ran), Collen Jones, Hong Ma. А так же спасибо за внимание и поддержку!

    Пожалуйста, свяжитесь со мной через GitHub или по электронной почте: \href{mailto:gao.xiang.thu@gmail.com}{gao.xiang.thu@gmail.com}.
\end{Russian}